\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2022-12-21 ms/adult.tex
Minor update

\FloatBarrier
%===============================================================================
% Supplementary Descriptives for sense of landscape of porn consumption
%===============================================================================
\section{Supplementary Descriptive Figures and Tables}
%============================
% Figure of top 25 adultsites
%============================
\begin{figure}[ht]
	\centering
	\caption{Top 25 Adult Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 adult sites that panelists visit in the sample period.
		Adult sites are categorized by YouGov.
		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  
		Sites to the right of the vertical dashed are the top 1 percent.
	}
	\label{fig:top25_adult}
\end{figure}

%================================
% Figure of top 25 non-adultsites
%================================
\begin{figure}
	\centering
	\caption{Top 25 (Non-Adult) Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 non-adult sites that panelists visit in the sample period.
		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  			
		Sites to the right of the vertical dashed are the top 1 percent.
	}
	\label{fig:top25_nonadult}
\end{figure}

%=============================================
% Figure for concentration of porn consumption
%=============================================
\begin{figure}
	\centering
	\caption{Traffic to Top 10 Porn Sites}
	\includegraphics[width=.5\textwidth]{../figs/concentration_porn_consumption.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The Top 10 bar indicates traffic to the top 10 adult sites in the data (see \cref{fig:top25_adult}).
		Time units is hours.
		Data is at the panelist-domain level.
		Others indicate traffic to all other adult sites outside of the top 10.
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption}
\end{figure}

%======================================================
% Figure for concentration of porn consumption by party
%======================================================
\begin{figure}
	\centering
	\caption{Traffic to Top 10 Porn Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The Top 10 bar indicates traffic to the top 10 adult sites in the data (see \cref{fig:top25_adult}).
		Time units is hours.
		Data is at the panelist-domain level.
		Others indicate traffic to all other adult sites outside of the top 10.
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_by_party}
\end{figure}

>>>>

\FloatBarrier
%===============================================================================
% Supplementary Descriptives for sense of landscape of porn consumption
%===============================================================================
\section{Supplementary Descriptive Figures and Tables}
%============================
% Figure of top 25 adultsites
%============================
\begin{figure}[ht]
	\centering
	\caption{Top 25 Adult Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 adult sites that panelists visit in the sample period.
		Adult sites are categorized by YouGov (see \textbf{subsection xx} discussion).
		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  
		Sites to the right of the vertical dashed are the top 1 percent of porn sites.
	}
	\label{fig:top25_adult}
\end{figure}

%================================
% Figure of top 25 non-adultsites
%================================
\begin{figure}
	\centering
	\caption{Top 25 (Non-Porn) Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 non-adult sites that panelists visit in the sample period.
		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  			
		Sites to the right of the vertical dashed are the top 1 percent (of non-porn sites).
	}
	\label{fig:top25_nonadult}
\end{figure}

%=============================================
% Figure for concentration of porn consumption
%=============================================
\begin{figure}
	\centering
	\caption{Traffic to Top 10 Porn Sites}
	\includegraphics[width=.5\textwidth]{../figs/concentration_porn_consumption.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The Top 10 bar indicates traffic to the top 10 adult sites in the data (see \cref{fig:top25_adult}).
		The Others bar indicates traffic to all other adult sites outside of the top 10.
		The y-axis is the total time spent on porn sites, averaged across individuals.
		Time units is hours.
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption}
\end{figure}

%======================================================
% Figure for concentration of porn consumption by party
%======================================================
\begin{figure}
	\centering
	\caption{Traffic to Top 10 Porn Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The Top 10 bar indicates traffic to the top 10 adult sites in the data (see \cref{fig:top25_adult}).
		The Others bar indicates traffic to all other adult sites outside of the top 10.
		The y-axis is the total time spent on porn sites, averaged across individuals.
		Time units is hours.
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_by_party}
\end{figure}
